 
 
#### happy
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('happy', indicator_table)
pind0  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'happy',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
happy
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind0$ci <- pind0$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind0$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### health
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('health', indicator_table)
pind26  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'health',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
health
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind26$ci <- pind26$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind26$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### imbgeco
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('imbgeco', indicator_table)
pind52  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'imbgeco',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
imbgeco
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind52$ci <- pind52$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind52$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### impcntr
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('impcntr', indicator_table)
pind78  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'impcntr',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
impcntr
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind78$ci <- pind78$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind78$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### imueclt
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('imueclt', indicator_table)
pind104  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'imueclt',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
imueclt
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind104$ci <- pind104$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind104$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### imwbcnt
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('imwbcnt', indicator_table)
pind130  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'imwbcnt',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
imwbcnt
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind130$ci <- pind130$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind130$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### polintr
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('polintr', indicator_table)
pind156  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'polintr',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
polintr
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind156$ci <- pind156$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind156$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### pplhlp
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('pplhlp', indicator_table)
pind182  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'pplhlp',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
pplhlp
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind182$ci <- pind182$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind182$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### stfeco
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('stfeco', indicator_table)
pind208  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'stfeco',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
stfeco
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind208$ci <- pind208$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind208$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### stfedu
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('stfedu', indicator_table)
pind234  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'stfedu',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
stfedu
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind234$ci <- pind234$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind234$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### stfhlth
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('stfhlth', indicator_table)
pind260  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'stfhlth',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
stfhlth
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind260$ci <- pind260$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind260$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### trstep
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('trstep', indicator_table)
pind286  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'trstep',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
trstep
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind286$ci <- pind286$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind286$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### trstlgl
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('trstlgl', indicator_table)
pind312  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'trstlgl',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
trstlgl
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind312$ci <- pind312$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind312$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### trstplc
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('trstplc', indicator_table)
pind338  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'trstplc',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
trstplc
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind338$ci <- pind338$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind338$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### trstun
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('trstun', indicator_table)
pind364  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'trstun',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
trstun
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind364$ci <- pind364$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind364$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### eisced2
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('eisced2', indicator_table)
pind390  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'eisced2',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
eisced2
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind390$ci <- pind390$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind390$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### stfgov2
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('stfgov2', indicator_table)
pind416  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'stfgov2',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
stfgov2
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind416$ci <- pind416$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind416$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### euftf2
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('euftf2', indicator_table)
pind442  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'euftf2',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
euftf2
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind442$ci <- pind442$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind442$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SH.XPD.GHED.GD.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SH.XPD.GHED.GD.ZS', indicator_table)
pind468  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SH.XPD.GHED.GD.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
SH.XPD.GHED.GD.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind468$ci <- pind468$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind468$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### NY.GDP.MKTP.KD
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('NY.GDP.MKTP.KD', indicator_table)
pind494  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'NY.GDP.MKTP.KD',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
NY.GDP.MKTP.KD
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind494$ci <- pind494$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind494$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### NY.GDP.MKTP.KD.ZG
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('NY.GDP.MKTP.KD.ZG', indicator_table)
pind520  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'NY.GDP.MKTP.KD.ZG',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
NY.GDP.MKTP.KD.ZG
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind520$ci <- pind520$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind520$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### NY.GDP.PCAP.KD
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('NY.GDP.PCAP.KD', indicator_table)
pind546  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'NY.GDP.PCAP.KD',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
NY.GDP.PCAP.KD
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind546$ci <- pind546$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind546$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### NY.GDP.PCAP.KD.ZG
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('NY.GDP.PCAP.KD.ZG', indicator_table)
pind572  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'NY.GDP.PCAP.KD.ZG',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
NY.GDP.PCAP.KD.ZG
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind572$ci <- pind572$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind572$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SE.XPD.TOTL.GD.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SE.XPD.TOTL.GD.ZS', indicator_table)
pind598  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SE.XPD.TOTL.GD.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
SE.XPD.TOTL.GD.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind598$ci <- pind598$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind598$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### IT.NET.USER.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('IT.NET.USER.ZS', indicator_table)
pind624  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'IT.NET.USER.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
IT.NET.USER.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind624$ci <- pind624$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind624$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SM.POP.TOTL.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SM.POP.TOTL.ZS', indicator_table)
pind650  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SM.POP.TOTL.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
SM.POP.TOTL.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind650$ci <- pind650$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind650$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SL.TLF.CACT.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SL.TLF.CACT.ZS', indicator_table)
pind676  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SL.TLF.CACT.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
SL.TLF.CACT.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind676$ci <- pind676$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind676$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### BX.TRF.PWKR.DT.GD.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('BX.TRF.PWKR.DT.GD.ZS', indicator_table)
pind702  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'BX.TRF.PWKR.DT.GD.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
BX.TRF.PWKR.DT.GD.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind702$ci <- pind702$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind702$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SP.POP.TOTL
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SP.POP.TOTL', indicator_table)
pind728  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SP.POP.TOTL',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
SP.POP.TOTL
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind728$ci <- pind728$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind728$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SM.POP.REFG
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SM.POP.REFG', indicator_table)
pind754  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SM.POP.REFG',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
SM.POP.REFG
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind754$ci <- pind754$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind754$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SP.RUR.TOTL.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SP.RUR.TOTL.ZS', indicator_table)
pind780  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SP.RUR.TOTL.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
SP.RUR.TOTL.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind780$ci <- pind780$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind780$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### GC.TAX.TOTL.GD.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('GC.TAX.TOTL.GD.ZS', indicator_table)
pind806  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'GC.TAX.TOTL.GD.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
GC.TAX.TOTL.GD.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind806$ci <- pind806$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind806$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SP.URB.TOTL.IN.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SP.URB.TOTL.IN.ZS', indicator_table)
pind832  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SP.URB.TOTL.IN.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
SP.URB.TOTL.IN.ZS
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind832$ci <- pind832$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind832$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### REFG.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('REFG.PCT', indicator_table)
pind858  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'REFG.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
REFG.PCT
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind858$ci <- pind858$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind858$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Refugee.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Refugee.PCT', indicator_table)
pind884  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Refugee.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
UNHCR.Refugee.PCT
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind884$ci <- pind884$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind884$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Asylum-.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Asylum-.PCT', indicator_table)
pind910  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Asylum-.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
UNHCR.Asylum-.PCT
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind910$ci <- pind910$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind910$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Interna.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Interna.PCT', indicator_table)
pind936  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Interna.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
UNHCR.Interna.PCT
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind936$ci <- pind936$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind936$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Statele.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Statele.PCT', indicator_table)
pind962  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Statele.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
UNHCR.Statele.PCT
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind962$ci <- pind962$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind962$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Other.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Other.PCT', indicator_table)
pind988  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Other.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = '
UNHCR.Other.PCT
',
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind988$ci <- pind988$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 7))
}
MyPrintInteractive(pind988$ci, plot_interactive, hover_css = 'stroke-width:3px;') 
 
```
 
 
