 
 
#### happy
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('happy', indicator_table)
pind0  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'happy',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind0$ci <- pind0$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind0$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### health
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('health', indicator_table)
pind24  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'health',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind24$ci <- pind24$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind24$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### imbgeco
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('imbgeco', indicator_table)
pind48  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'imbgeco',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind48$ci <- pind48$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind48$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### impcntr
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('impcntr', indicator_table)
pind72  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'impcntr',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind72$ci <- pind72$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind72$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### imueclt
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('imueclt', indicator_table)
pind96  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'imueclt',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind96$ci <- pind96$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind96$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### imwbcnt
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('imwbcnt', indicator_table)
pind120  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'imwbcnt',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind120$ci <- pind120$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind120$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### polintr
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('polintr', indicator_table)
pind144  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'polintr',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind144$ci <- pind144$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind144$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### pplhlp
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('pplhlp', indicator_table)
pind168  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'pplhlp',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind168$ci <- pind168$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind168$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### stfeco
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('stfeco', indicator_table)
pind192  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'stfeco',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind192$ci <- pind192$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind192$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### stfedu
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('stfedu', indicator_table)
pind216  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'stfedu',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind216$ci <- pind216$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind216$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### stfhlth
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('stfhlth', indicator_table)
pind240  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'stfhlth',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind240$ci <- pind240$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind240$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### trstep
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('trstep', indicator_table)
pind264  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'trstep',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind264$ci <- pind264$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind264$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### trstlgl
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('trstlgl', indicator_table)
pind288  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'trstlgl',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind288$ci <- pind288$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind288$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### trstplc
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('trstplc', indicator_table)
pind312  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'trstplc',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind312$ci <- pind312$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind312$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### trstun
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('trstun', indicator_table)
pind336  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'trstun',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind336$ci <- pind336$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind336$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### eisced2
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('eisced2', indicator_table)
pind360  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'eisced2',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind360$ci <- pind360$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind360$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### stfgov2
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('stfgov2', indicator_table)
pind384  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'stfgov2',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind384$ci <- pind384$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind384$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### euftf2
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('euftf2', indicator_table)
pind408  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'euftf2',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind408$ci <- pind408$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind408$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SH.XPD.GHED.GD.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SH.XPD.GHED.GD.ZS', indicator_table)
pind432  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SH.XPD.GHED.GD.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind432$ci <- pind432$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind432$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### NY.GDP.MKTP.KD
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('NY.GDP.MKTP.KD', indicator_table)
pind456  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'NY.GDP.MKTP.KD',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind456$ci <- pind456$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind456$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### NY.GDP.MKTP.KD.ZG
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('NY.GDP.MKTP.KD.ZG', indicator_table)
pind480  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'NY.GDP.MKTP.KD.ZG',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind480$ci <- pind480$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind480$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### NY.GDP.PCAP.KD
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('NY.GDP.PCAP.KD', indicator_table)
pind504  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'NY.GDP.PCAP.KD',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind504$ci <- pind504$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind504$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### NY.GDP.PCAP.KD.ZG
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('NY.GDP.PCAP.KD.ZG', indicator_table)
pind528  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'NY.GDP.PCAP.KD.ZG',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind528$ci <- pind528$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind528$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SE.XPD.TOTL.GD.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SE.XPD.TOTL.GD.ZS', indicator_table)
pind552  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SE.XPD.TOTL.GD.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind552$ci <- pind552$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind552$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### IT.NET.USER.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('IT.NET.USER.ZS', indicator_table)
pind576  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'IT.NET.USER.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind576$ci <- pind576$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind576$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SM.POP.TOTL.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SM.POP.TOTL.ZS', indicator_table)
pind600  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SM.POP.TOTL.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind600$ci <- pind600$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind600$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SL.TLF.CACT.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SL.TLF.CACT.ZS', indicator_table)
pind624  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SL.TLF.CACT.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind624$ci <- pind624$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind624$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### BX.TRF.PWKR.DT.GD.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('BX.TRF.PWKR.DT.GD.ZS', indicator_table)
pind648  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'BX.TRF.PWKR.DT.GD.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind648$ci <- pind648$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind648$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SP.POP.TOTL
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SP.POP.TOTL', indicator_table)
pind672  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SP.POP.TOTL',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind672$ci <- pind672$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind672$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SM.POP.REFG
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SM.POP.REFG', indicator_table)
pind696  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SM.POP.REFG',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind696$ci <- pind696$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind696$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SP.RUR.TOTL.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SP.RUR.TOTL.ZS', indicator_table)
pind720  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SP.RUR.TOTL.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind720$ci <- pind720$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind720$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### GC.TAX.TOTL.GD.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('GC.TAX.TOTL.GD.ZS', indicator_table)
pind744  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'GC.TAX.TOTL.GD.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind744$ci <- pind744$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind744$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### SP.URB.TOTL.IN.ZS
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('SP.URB.TOTL.IN.ZS', indicator_table)
pind768  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'SP.URB.TOTL.IN.ZS',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind768$ci <- pind768$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind768$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### REFG.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('REFG.PCT', indicator_table)
pind792  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'REFG.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind792$ci <- pind792$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind792$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Refugee.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Refugee.PCT', indicator_table)
pind816  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Refugee.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind816$ci <- pind816$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind816$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Asylum-.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Asylum-.PCT', indicator_table)
pind840  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Asylum-.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind840$ci <- pind840$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind840$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Interna.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Interna.PCT', indicator_table)
pind864  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Interna.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind864$ci <- pind864$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind864$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Statele.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Statele.PCT', indicator_table)
pind888  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Statele.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind888$ci <- pind888$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind888$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
#### UNHCR.Other.PCT
 
```{r, echo=FALSE, warning=FALSE}
this_ind <- GetIndicator('UNHCR.Other.PCT', indicator_table)
pind912  <- MakeIndicatorCountryPlot(
ds = ds_ss_avg_cntry_ind,
id_term = 'UNHCR.Other.PCT',
cntry_term = 'cntry_name',
year_term = 'ess_year',
txt_head = as.character(this_ind$name),
txt_subhead = indicator_short,
txt_caption = paste(as.character(this_ind$source), '2002-2016'),
show_summary = TRUE,
plevel = p_val)
if (!is.na(this_ind$lblmin)){
pind912$ci <- pind912$ci +
ylab(paste(this_ind$lblmin, this_ind$min, '<-->', this_ind$lblmax, this_ind$max)) +
theme(axis.title.y = element_text(size = 9))
}
MyPrintInteractive(pind912$ci, create_interactive_plot, hover_css = 'stroke-width:3px;') 
 
```
 
 
